Chi-squared test example using `nycflights13` `flights` data

### 2018-04-11 inst/doc/chisq_test.Rmd

The observed $t$ statistic is `r obs_chisq`.

@@

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # calculate(stat = "Chisq") ## Not needed since Chisq is implied
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

>>>>

@@

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # generate() ## Not used for theoretical
  calculate(stat = "Chisq") %>%
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```
